---
title: "Group2_Assignment1_Code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Import Packages

```{r}
pacman::p_load(
  tidyverse,
  here,
  ggplot2,
  dplyr,
  knitr,
  stargazer,
  DescTools,
  lmtest,
  sandwich,
  car
)
```

# Step 2

## Comfirm your assigned dataset and paper

```{r}
# Import Dataset

data0 <- read.csv(here("data_raw", "05_DATA0.csv"))

data2 <- read.csv(here("data_raw", "05_DATA2.csv"))
```

## Data origin and extension

```{r}
# Clean Dataset

merged_df <- inner_join(data0, data2, by = c("fips", "year", "kfact")) %>% 
  # Combine data0 and data2 based on 'fips', 'year' and "kfact. 
  # We combine based on multiple columns because we want to combine based on primary key
  drop_na() %>% 
  select("year", "fips", "rprofit_acre", "moist.y", "dry", "kfact", "mean_t04", "mean_t05", "mean_t06", "mean_t07", "mean_t08", "mean_t09", "mean_p04", "mean_p05", "mean_p06", "mean_p07", "mean_p08", "mean_p09") %>% # select dependent variable and independent variables from merged dataframe
  mutate(Mean_Temperature = rowMeans(across(mean_t04 : mean_t09))) %>% # Convert Monthly Temperature to Yearly 
  mutate(Mean_Precipitation = rowMeans(across(mean_p04 : mean_p09))) %>% # Convert Montly Precipitation to Yearly
  select(-mean_t04 : -mean_p09) %>% # Drop useless temperature and percipitation variables
  mutate(Temp_Dummy = if_else(Mean_Temperature >= 46.2 & Mean_Temperature <= 93.2, 1, 0)) %>% 
  # Create Dummy variable for mean temperature.
  # When the mean temperature is within the range, dummy variable is 1, otherwise dummy variable is 0
  rename(Year = year, County  = fips, Profit_per_Acre = rprofit_acre, 
        Moist = moist.y, Dry = dry, Soil_Erosion = kfact)
```

```{r}
head(merged_df)
```

## Correlation Analysis

```{r}
correlation_variables <- merged_df %>% 
  select(Profit_per_Acre, Moist, Dry, Soil_Erosion, Mean_Temperature, Mean_Precipitation, Temp_Dummy)

# Calculate Correlation 
cor_analysis <- cor(correlation_variables, use = "pairwise.complete.obs")

# Define variable names
var_names <- c("Profit", "Moist", "Dry", "Erosion", "Temp", "Precip", "TempDummy")

rownames(cor_analysis) <- var_names
colnames(cor_analysis) <- var_names

stargazer(cor_analysis,
          title = "Correlation Analysis",
          align = TRUE,
          type = 'text',
          rownames = TRUE,
          colnames = TRUE,
          header = FALSE,
          font.size = "small"
          )
```
## Scatter Plots and Outliers Check

```{r}
# Profit per Acre v.s. Moist

profit_moist_scatter <- merged_df %>% 
  ggplot(aes(x = Moist, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Moist",
       x = "Moist",
       y = "Profit per Acre"
       )
profit_moist_scatter
```

```{r}
# Profit per Acre v.s.Dry

profit_dry_scatter <- merged_df %>% 
  ggplot(aes(x = Dry, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Dry",
       x = "Dry",
       y = "Profit per Acre"
       )
profit_dry_scatter

```

```{r}
# Profit per Acre v.s.Mean Temperature

profit_temp_scatter <- merged_df %>% 
  ggplot(aes(x = Mean_Temperature, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Mean Temperature",
       x = "Mean Temperature (Growing Season)",
       y = "Profit per Acre"
       )
profit_temp_scatter
```

```{r}
# Profit per Acre v.s.Mean Precipitation

profit_prec_scatter <- merged_df %>% 
  ggplot(aes(x = Mean_Precipitation, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Mean Precipitation",
       x = "Mean Precipitation",
       y = "Profit per Acre"
       )
profit_prec_scatter
```

```{r}
# Profit per Acre v.s.Temperature Dummy

profit_temp_dummy_scatter <- merged_df %>% 
  ggplot(aes(x = Temp_Dummy, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Temperature Dummy",
       x = "Temperature Dummy",
       y = "Profit per Acre"
       )
profit_temp_dummy_scatter
```

```{r}
# Profit per Acre v.s.Soil Erosion

profit_erosion_scatter <- merged_df %>% 
  ggplot(aes(x = Soil_Erosion, y = Profit_per_Acre)) +
  geom_point(alpha = 0.7,color = "#40BDBB") +
  labs(title = "Scatter Plot of Profit per Acre v.s. Soil Erosion",
       x = "Soil Erosion",
       y = "Profit per Acre"
       )
profit_erosion_scatter
```

```{r}
# Histogram of Profit per Acre
# We have seen Profit per Acre has some outliers based on scatter plots
# So we want to use histogram to check the distribution of Profit per Acre, so we would know which outliers handling method we should use

hist_profit <- merged_df %>% 
  ggplot(aes(x = Profit_per_Acre)) +
  geom_histogram(bins = 50, fill = "#69b3a2", alpha=0.9) +
  coord_cartesian(xlim = c(-500000, 500000)) +
  labs(title = "Distribution of Profit per Acre",
       x = "Profit per Acre",
       y = "Count") +
  theme_minimal() +
  theme(
  plot.title = element_text(size=15)
)
hist_profit
```

```{r}
# Use Winsorization to handle outliers
# The histogram shows Profit per Acre is right skewed

merged_df_win <- merged_df %>% 
  mutate(
    Profit_per_Acre_Win = Winsorize(
      Profit_per_Acre, 
      val = quantile(Profit_per_Acre, probs = c(0.01, 0.9), na.rm = TRUE)
      )
  ) %>% 
  select(-Profit_per_Acre)

```

## Summary Statistics

```{r}
vars_for_stats <- c("Profit_per_Acre_Win", "Moist", "Dry", "Soil_Erosion", 
                    "Mean_Temperature", "Mean_Precipitation", "Temp_Dummy", "County")

stargazer(merged_df_win[, vars_for_stats],
          type = "text",
          title = "Descriptive Statistics",
          digits = 2
          )
```

## Multiple Regression Models

```{r}
# Build regression models

m0 <- lm(Profit_per_Acre_Win ~ Mean_Temperature + Mean_Precipitation, data = merged_df_win)
m1 <- lm(Profit_per_Acre_Win ~ Mean_Temperature + Mean_Precipitation + Moist, data = merged_df_win)
m2 <- lm(Profit_per_Acre_Win ~ Mean_Temperature + Mean_Precipitation + Moist + Dry, data = merged_df_win)
m3 <- lm(Profit_per_Acre_Win ~ Mean_Temperature + Mean_Precipitation + Moist + Dry + Soil_Erosion, data = merged_df_win)

```

```{r}
# Regression Table

stargazer(m0, m1, m2, m3,
          type = "text",                
          title = "Multiple Regression Models",
          digits = 3,                    
          column.labels = c("Model 0", "Model 1", "Model 2", "Model 3"),
          dep.var.labels = "Profit per Acre (Winsorized)"
)
```

## Diagnostics and remedies

```{r}
# Check each model VIF

print(vif(m0))
print(vif(m1))
print(vif(m2))
print(vif(m3))
```

```{r}
# Heteroskedasticity
# Breusch–Pagan test

print(bptest(m0))
print(bptest(m1))
print(bptest(m2))
print(bptest(m3))

```
Since all of our p-values are smaller than 0.05, we need to use robust SE

```{r}
# F-test

anova(m0, m1, m2, m3)

```

```{r}
# RESET-test

print(resettest(m0))
print(resettest(m1))
print(resettest(m2))
print(resettest(m3))

```

```{r}
# Residual Plot
# m3

par(mfrow=c(1,1))      # Show 4 plots together: c(2,2)
plot(m3)               # Produces: residuals vs fitted, QQ, scale-location, residuals vs leverage plots

# Residuals vs Fitted (plot 1)
plot(m3, which = 1)

# Normal Q-Q plot of residuals (plot 2)
plot(m3, which = 2)

# Scale-Location plot (plot 3)
plot(m3, which = 3)

# Residuals vs Leverage plot (plot 5)
plot(m3, which = 5)

```

## Robustness check

```{r}
# Re-estimate the final full model

m0r <- coeftest(m0, vcov = vcovHC(m0, type = "HC1"))
m1r <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
m2r <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
m3r <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))

```

```{r}
# Robustness Regression Table

stargazer(m0r, m1r, m2r, m3r,
          type = "text",                
          title = "Multiple Regression Models",
          digits = 3,                    
          column.labels = c("Model 0", "Model 1", "Model 2", "Model 3"),
          dep.var.labels = "Profit per Acre (Winsorized)"
)
```




# Crate scatter plots for all chosen variables (dependent variable v.s. independent variables)





